Towards Verifying the Bitcoin-S Library

### 2019-06-20 paper/paper.tex
auto linebreak for style stainless

\lstdefinestyle{stainless}{numbers=none, breaklines=false,  basicstyle=\footnotesize\ttfamily,}

@@

Stainless output:
{\footnotesize
\begin{verbatim}
  [ Error  ] Code.scala:41:1: Objects cannot extend classes or implement traits,
             use a case object instead
           object Int64 extends BaseNumbers[Int64] {
           ^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^...
  [ Error  ] Code.scala:84:1: Objects cannot extend classes or implement traits,
            use a case object instead
            object Satoshis extends BaseNumbers[Satoshis] {
            ^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^...
\end{verbatim}}

@@

>>>>

\lstdefinestyle{stainless}{
  numbers=none,
  breaklines=true,
  breakautoindent=true,
  breakindent=63pt,
  basicstyle=\footnotesize\ttfamily
}

@@

Stainless output:
\begin{lstlisting}[style=stainless]
  [ Error  ] currency/CurrencyUnits.scala:33:1: Objects cannot extend classes or implement traits, use a case object instead
            object Satoshis extends BaseNumbers[Satoshis] {
            ^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^...
  [ Error  ] number/NumberType.scala:65:1: Objects cannot extend classes or implement traits, use a case object instead
            object Int64 extends BaseNumbers[Int64] {
            ^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^...
\end{lstlisting}

Code before:
\begin{lstlisting}[style=scala]
object Int64 extends BaseNumbers[Int64] { ... }
object Satoshis extends BaseNumbers[Satoshis] { ... }
\end{lstlisting}

Code after:
\begin{lstlisting}[style=scala]
case object Int64 extends BaseNumbers[Int64] { ... }
case object Satoshis extends BaseNumbers[Satoshis] { ... }
\end{lstlisting}

@@

\todo{Ramon does this change semantics?}
